Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654

### 2016-06-22 WRITEUP/ms.tex
add de-lensed FWHM

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We detected the \bco line emission toward the background galaxies
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
179$\pm$9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis} \label{sec:anal}
\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the images are resolved over
$\sim$2 resolution elements. Given the extent of the lensed emission,
this implies that our \bco observations do not resolve
structures (e.g. knots and arcs) of the lensed emission
(i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Models of each slice thus provide the
properties on the intrinsic kinematics. To increase the SNR for modeling, the
slices are obtained by binning five native channels
($\Delta v$\,$\sim$\,21.5\kms) over the full
linewidth of $\sim$750\,\kms in the original data, resulting in seven
independent channels.

@@

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also coincides with this component F. It is therefore evident that we
detect \bco emission in the companion galaxy.
To quantify the type of merger (major v.s. minor) conventionally with a mass
ratio, we decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
use the best-fit flux densities and magnification factors obtained
from the model of this channel to derive the intrinsic gas mass in the companion.
Assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1 and
a CO luminosity-to-H2 mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, we find 
a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun. 
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun,
implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a ``wet-wet'' minor merger according to
the classification scheme commonly used in literature.

@@

\input{table_magFactor}
Similar to previous studies of RXJ1131, where
differential lensing across {\it HST}
$V$-, $I$-, and $H$-band has been detected with a
magnification factor decreasing from 10.9 to 7.8 (C06),
the highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component and the asymmetric line profile.   
To first order, this can be explained by the difference in magnification factor which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}).  % also because of a contribution from the companion in the observed, lensed spectrum
Such an effect (difference in $\mu_{\rm L}$ across channels) is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing 
emission mainly originates near the cusp 
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and 
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively, 
implying an intrinsically symmetric line profile. This is consistent with the source-plane
velocity gradient in our lens model (see \Sec{caveat}). 
% The difference in magnification factors between CO and optical-to-NIR emission
% may further indicate that the CO emitting region is more extended than .

\subsection{\bco Kinematics}
A clear velocity gradient and a high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion may hint
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. 
Therefore, in this scenario, RXJ1131 is 
likely a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.

@@

% assuming virialized gas
%Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
%within the CO-emitting region. If we instead consider the
%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
%We correct for the inclination effect using the
%morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
%from the reconstructed image (Figure 3 in C06), yielding
%an inclination angle of 56.4\degr, which is consistent with the
%observed unobscured AGN and an observable double peak line profile.
%The dynamical mass is then
%8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
%Since this quantity is derived under the assumption that the gas is
%virialized, which is highly unlikely given the velocity dispersion and the
%presence of a close companion, our estimate is
%at most an upper limit.

@@

\subsection{Gas Properties} \label{sec:properties}
In this section, we derive the gas properties of the merger system
based on \bco and compare with those reported by
C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
and using a different definition of
\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention, 
we find a \fir luminosity of 
\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.}.
% the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
We note that their results are based on \bco and \rot{4}{3} line observations with the 
IRAM 30-m single-dish telescope.

@@

\subsubsection{SFE and Depletion Time}
We derive the SFE using the far-IR luminosity definition used by
C13 (\ie SFE\pmm\LFIR$($40\,$-$\,500\,\micron)$/$$M_{\rm gas}$$)$,
we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
timescale of $\tau$\,=\,190\pmm70\,Myr. % 5.8/SFE Gyr
This SFE is substantially lower than most U/LIRGs
(\citealt{Solomon97a,Combes11a}; C13). % local ULIRG: 180 +/- 160 Lsun/M (Solomon+97)
% Combes+13: sample of 39 gal from z= 0.2-1 find $<$ 100 Myr.

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\subsection{Merger stage of RXJ1131-1231}
In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a
gas-rich companion, but how does this affect its internal dynamics?
What is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.

@@

@@

@@

@@

Facilities: IRAM PdBI, CARMA, VLA, Herschel (SPIRE), WISE, IRAS, 2MASS, Spitzer(IRAC, MIPS), HST(ACS, NICMOS)

>>>>

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We detected the \bco line emission toward the background galaxies
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis} \label{sec:anal}
%\subsection{Stellar Mass and BH-Bulge Mass Correlation}
%Rest-frame $K$-band (NIR) photometry has been proposed as a reliable proxy to
%the underlying total stellar mass. Using the decomposed IRAC photometry at 3.6$\micron$ (rest-frame $K$-band), 
%we find a stellar mass of BLAH, using the BLAH.
%This implies a $M_{\rm BH}$$/$$M^*$ = BLAH (cf. $\sim$0.1\% found in local galaxies).
%
%The AGN-starburst connection has become a central issue with the discovery of the relation
%between stellar velocity dispersion and mass of the central black hole in spheroidal stellar
%systems (Magorrian et al. 1998, Ferrarese & Merritt 2000, Gebhardt et al. 2000). Given that
%elliptical galaxies are mainly old, this relation has to be put in place at their formation history.
%
%This implies that RXJ1131 is in the BLAH stage of the evolution, in which the BH ?.

\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the images are resolved over
$\sim$2 resolution elements. Given the extent of the lensed emission,
this implies that our \bco observations do not resolve
structures (e.g. knots and arcs) of the lensed emission
(i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Models of each slice thus provide the
properties on the intrinsic kinematics. To increase the SNR for modeling, the
slices are obtained by binning five native channels
($\Delta v$\,$\sim$\,21.5\kms) over the full
linewidth of $\sim$750\,\kms in the original data, resulting in seven
independent channels.

@@

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc in projection from the AGN host galaxy,
and C06, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also coincides with this component F. It is therefore evident that we
detect \bco emission in the companion galaxy.

To quantify the type of merger (major v.s. minor) conventionally with a mass
ratio, we decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
use the best-fit flux densities and magnification factors obtained
from the model of this channel to derive the intrinsic gas mass in the companion.
Assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1 and
a CO luminosity-to-$H_2$ mass conversion factor of
\alphaco\,=\,0.8 $($K \kms pc$^2$$)$\pmOne, we find 
a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun. 
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun,
implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a {\em ``wet-wet'' minor merger} according to
the classification scheme commonly used in literature.

@@

\input{table_magFactor}
Similar to previous studies of RXJ1131, where
differential lensing across {\it HST}
$V$-, $I$-, and $H$-band has been detected with a
magnification factor decreasing from 10.9 to 7.8 (C06),
the highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component and the asymmetric line profile.   
This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}) and also partly due to a contribution from the companion in the redshifted velocity channels.
The variation in $\mu_{\rm L}$ across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing 
emission mainly originates near the cusp 
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and 
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively, 
implying an intrinsically symmetric line profile. This is consistent with the source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}). 
% The difference in magnification factors between CO and optical-to-NIR 
% may further indicate that the CO emitting region is more extended and/or 
% has a spatial offset from the optical-to-NIR emission 
% (\ie different positions and alignment relative to the caustics) given 
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5) 
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and 
% the degeneracy between the intrinsic source size and the magnification factor.

\subsection{\bco Kinematics} 
Fitting a four-parameter double-Gaussian that describes two velocity peaks by a single FWHM
to the ``intrinsic" \bco line profile of RXJ1131 (after correcting for lensing using 
the magnification factors for various channels and separating the emission from RXJ1131 and its companion),
we find a roughly symmetric double-horned profile with a flux ratio of 1.2\pmm0.4 between the peaks, which 
are separated by
$\Delta v_{\rm sep}$ = 387\pmm45\,\kms, and a 
FWHM of 220\pmm72\,\kms. 
If we instead fit with a single-Gaussian, we find a FWHM of 600\pmm160\,\kms for RXJ1131
and 73\pmm43\,\kms for the companion galaxy.

A clear velocity gradient and a high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion may hint
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. 
Therefore, in this scenario, RXJ1131 is 
likely a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.

@@

@@

\subsection{ISM Properties} \label{sec:properties}
In this section, we derive the gas properties of the merger system
based on \bco and compare with those reported by
C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
and using a different definition of
\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention, 
we find a \fir luminosity of 
\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.}.
% the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
We note that their results are based on \bco and \rot{4}{3} line observations with the 
IRAM 30-m single-dish telescope.

 \subsubsection{Dynamical Mass}
 Assuming the \bco gas dynamically BLAH. 
%% assuming virialized gas
Using our $V_{\rm rot}$ estimated from dynamical modeling in \Sec{dynamics}, 
we find a dynamical mass of
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
within the CO-emitting region in RXJ1131. If we instead consider the
\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
We correct for the inclination effect using the
morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
from the reconstructed image (Figure 3 in C06), yielding
an inclination angle of 56.4\degr, which is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then
8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
Since this quantity is derived under the assumption that the gas is virialized in a  % rotatioally supported
spherical distribution, \ie using 
\begin{equation}
M_{\rm dyn} \sin^2 i = \frac{\Delta v^2 R}{G},
\end{equation}
our estimate is at most an upper limit given the observed velocity dispersion and the
presence of a close companion.
COMPARE with Stellar MASS.

Similarly, we estimate the dynamical mass in the companion under the same assumptions. 
For $\Delta v$, we use the FWHM linewidth obtained by fitting a single Gaussian to the pseudo 
\bco line profile obtained by decomposing its contribution to the total line flux using the magnification factor
found for the model of corresponding velocity channel.
Assuming a source size of $\sim$700 pc inferred from the lens model of {\it HST} $V$-band (B08).
This yields $M_{\rm dyn}$\,$\sin^2 i$ = BLAH \Msun.
If we assume an average inclination angle of $<\sin i>^2$ = BLAH, we find $M_{\rm dyn}$ = BLAH \Msun.

@@

\subsubsection{Conversion Factor $\alpha_{\rm CO}$}
Instead of adopting the conversion factor $\alpha_{\rm CO}$ as 0.8 (K \kms pc$^2$)\pmOne,
a crude estimate can be obtained using the dust mass and CO luminosity, assuming a 
gas-to-dust ratio.
Here we assume a gas-to-dust ratio of 72 (Sandstrom+13), based on a sample of local star-forming
galaxies of solar metallicities. 
We find $\alpha_{\rm CO}$ = BLAH\pmm$(f_{\rm gas-dust}/72)$ (K \kms pc$^2$)\pmOne, where the uncertainty does not include 
systematic uncertainties 
in the dust absorption coefficient $(\kappa)$ and the gas-to-dust ratio.
% which Kapa? Kappa 870 or Kappa we used in our dust mass esimate?
This ?

\subsubsection{SFE and Depletion Timescales}
We derive the SFE using the far-IR luminosity definition used by
C13 (\ie SFE\pmm\LFIR$($40\,$-$\,500\,\micron)$/$$M_{\rm gas}$$)$,
we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
timescale of $\tau$\,=\,190\pmm70\,Myr. % 5.8/SFE Gyr
This SFE is substantially lower than most U/LIRGs
(\citealt{Solomon97a,Combes11a}; C13). % local ULIRG: 180 +/- 160 Lsun/M (Solomon+97)
% Combes+13: sample of 39 gal from z= 0.2-1 find $<$ 100 Myr.

@@

At high redshifts, SMGs the irregular, turbulent starbursting galaxies (SFR $\sim$ BLAH \Msun yr\pmOne)
and BzK are the ``normal" star-forming disk galaxies with low SFE, relatively high SFR (BLAH) and 
longer depletion time (BLAH Myr).

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\subsection{Merger stage of RXJ1131-1231}
Using the redshift inferred from the line center of the CO gas disk $(z_{\rm CO} = 0.6537)$ 
as the systemic redshift. The velocity offset from the optical lines $(z_{\rm AGN} = 0.658)$ 
is $\sim$780\,\kms. This may ? interaction

In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a
gas-rich companion, but how does this affect its internal dynamics?
What is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.

@@

\subsection{Morphological Transformation}
While the space density of ULIRGs are only BLAH Mpc$^{-3}$ (CITE), 
the blah and the evolution in structure of high- and low-z galaxies
implying ULIRGs and mergers play an important role in giving rise to the BLAH.

@@

which seem probable given the relation in AGN growth and gas accumulation.
the simultaneous observation of the AGN phenomenon, of stellar formation and of galaxy interaction illustrates the current AGN ? black hole paradigm, according to which the growth of a black hole through the AGN phase occurs when galaxy interactions provide gas inflow towards the center (e.g. Hernquist 1989; Di Matteo et al. 2005). Since the interactions induce gravitational perturbations, simultaneous starbursts are also expected.

@@

The compactness of the emission in $V$-band (rest-frame UV) 
suggests that the \SF in RXJ1131 is proceeding in a 
compact region embedded w/in a large reservoir of molecular gas, which may be explained 
by gas inflow toward nuclear regions due to interaction with the companion. 
Such a scenario may support the results in recent models: mergers/ULIRGs evolve into bulge dominated massive disks (Geach+09 sect 3.4).

@@

Facilities: IRAM PdBI, CARMA, VLA, Herschel(SPIRE), WISE, IRAS, 2MASS, Spitzer(IRAC, MIPS), HST(ACS, NICMOS)
